\renewcommand\bibname{\textbf{Referencias}}
\begin{thebibliography}{99}

\addcontentsline{toc}{chapter}{Referencias}
\chead{Referencias}

\bibitem{1} Matthew J. Lehner, Shiang-Yu Wang, Charles A. Alcock, Kem H. Cook, Gabor Furesz, John C. Geary, David Hiriart, Paul T. Ho, William H. Lee, Frank Melsheimer, Timothy Norton, Mauricio Reyes-Ruiz, Michael Richer, Andrew Szentgyorgyi, Wei-Ling Yen a and Zhi-Wei Zhang,  \textit{Status of the Transneptunian Automated Occultation Survey (TAOS II)}. SPIE (2014)

\bibitem{2} Luu, J. X. and Jewitt, D. C., \textit{Kuiper belt objects: Relics from the Accretion Disk of the Sun,} ARA\& A 40, 63-101 (2002)

\bibitem{3} Lehner, M. J. et al.,  \textit{The TAOS Project: Statistical Analysis of Multi-Telescope Time Series Data}. PASP 122, 959-975 (2010).

\bibitem{4} Arfken, G. B., Weber, H.-J., \& Harris, F. \textit{Mathematical methods for physicists: A comprehensive guide}. Waltham, MA: Academic Press/Elsevier (2013).

\bibitem{5} D. Ricci, F. G. Ramon-Fox, C. Ayala-Loera, R. Michel, S. Navarro-Meza, L. Fox-Machado y M. Reyes-Ruiz \textit{Multifilter transit observations of WASP-39b and WASP-43b with three San Pedro Mártir telescopes}, Astronomical Society of the Pacific,127:143-151 (2015)

\bibitem{6} Hellier, C., Anderson, D. R., Collier Cameron, A., et al. \textit{Three WASP-South transiting exoplanets: WASP-74b, WASP-83b \& WASP-89b}. AJ, submitted, ArXiv e-prints [arXiv:1410.6358] (2014)

\bibitem{7} Street, R. A. \& SuperWASP Consortium \textit{SuperWASP: Wide-Angle Search for Planets}. Baltic Astronomy, Vol. 13, p. 707-710 (2004)

\bibitem{8} Bakos, G.A., Hartman, J. D., Torres, G., et al.\textit{HAT-P-34b-HAT-P-37b: Four transiting planets more massive than Jupiter orbiting moderately bright stars}. AJ, 144,19 (2010)

\bibitem{9} Bakos, G.; Noyes, R. W.; Kovács, G.; Stanek, K. Z.; Sasselov, D. D.; Domsa, I. \textit{Wide-Field Millimagnitude Photometry with the HAT: A Tool for Extrasolar Planet Detection}, Astronomical Society of the Pacific, Volume 116, Issue 817, pp. 266-277. (2004)

\bibitem{10} Z.-W. Zhang, M.J. Lehner, J.-H. Wang, C.-Y. Wen, S.-Y. Wang, S.-K. King, A.P. Granados, C. Alock, T. Axelrod, F. B. Bianco, Y.-I. Byun, W. P. Chen, N. K. Coehlo, K. H. Cook, I. de Pater, D.-W. Kim, T. Lee, J. J. Lissauer, S.L. Marshall, P. Protopapas, J. A. Rice, y M. E. Schwamb,  \textit{The TAOS project: results from seven years
of survey data}. The Astronomical Jurnal, 146, 1, 14. (2013)


\bibitem{11} Dae-Won Kim, \textit {De-Trending Time Series for Astronomical Variability Surveys}, Astronomical Society of the Pacific, 2009, p.247 

\bibitem{12} Mandel, K., \& Agol, E., \textit{Analityc light curves for planetary transit searches}, ApJ, 580, L171 (2002)

\bibitem{13} Kreidberg, L. \textit{batman: BAsic Transit Model cAlculatioN in Python}, PASP, 127, 1161 (2015)


\bibitem{14} Cesar. A. Villareal, Mauricio Reyes-Ruiz \textit{Detectabilidad y Probabilidad de Detección de Exoplanetas en el Proyecto TAOS II} 2do. TALLER NACIONAL DE ASTROFÍSICA PLANETARIA. UANL, Monterrey, N.L. 10 al 13 de marzo de 2015.

\bibitem{15} S. Brown Sevilla, \textit{Study of exoplanetary transits of KELT-1b and WASP-33b observed with the San Pedro Mártir 84 cm telescope (2015)}








\end{thebibliography}
